### 2016-03-24 docs/online_supporting_information.Rmd
fixers typo in growth rate prediction equations

\noindent where $p_i$ is the average frequency of species *i*, $p_i = N_i/N_T$.
When all species have identical abundances and $p_i = 1/S$, where *S* is species richness, the both synchrony values equal 1/S [@Loreau2008a]. The prediction represented in Equation S20 is Equation 3 in the main text, which we refer to as $\phi_{R,\mathcal{M}_D}$.

@@

\begin{equation}
\phi_R = \frac{\sum_{i,j} p_i p_j \text{cov}(u_{ei}, u_{ej})}{S^2}
\end{equation}

\noindent The prediction represented in Equation S22 is Equation 4 in the main text, which we refer to as $\phi_{R,\mathcal{M}_E}$. If we know the covariance matrix of the species environmental responses, we can calculate the above expectations directly. Note that the environmental responses are normalized in the above equations, therefore the covariances are correlations in the above equations.

>>>>

\noindent where $p_i$ is the average frequency of species *i*, $p_i = N_i/N_T$.
When all species have identical abundances and $p_i = 1/S$, where *S* is species richness, the both synchrony values equal 1/S [@Loreau2008a]. The prediction represented in Equation S19 is Equation 3 in the main text, which we refer to as $\phi_{R,\mathcal{M}_D}$.

@@

\begin{equation}
\phi_R = \frac{\sum_{i,j} \text{cov}(u_{ei}, u_{ej})}{S^2}
\end{equation}

\noindent The prediction represented in Equation S21 is Equation 4 in the main text, which we refer to as $\phi_{R,\mathcal{M}_E}$. If we know the covariance matrix of the species environmental responses, we can calculate the above expectations directly. Note that the environmental responses are normalized in the above equations, therefore the covariances are correlations in the above equations.

### 2016-03-24 docs/online_supporting_information.tex
fixers typo in growth rate prediction equations

\noindent where \(p_i\) is the average frequency of species \emph{i},
\(p_i = N_i/N_T\). When all species have identical abundances and
\(p_i = 1/S\), where \emph{S} is species richness, the both synchrony
values equal 1/S (Loreau and {{de Mazancourt}} 2008). The prediction
represented in Equation S20 is Equation 3 in the main text, which we
refer to as \(\phi_{R,\mathcal{M}_D}\).

@@

\begin{equation}
\phi_R = \frac{\sum_{i,j} p_i p_j \text{cov}(u_{ei}, u_{ej})}{S^2}
\end{equation}

\noindent The prediction represented in Equation S22 is Equation 4 in
the main text, which we refer to as \(\phi_{R,\mathcal{M}_E}\). If we
know the covariance matrix of the species environmental responses, we
can calculate the above expectations directly. Note that the
environmental responses are normalized in the above equations, therefore
the covariances are correlations in the above equations.

>>>>

\noindent where \(p_i\) is the average frequency of species \emph{i},
\(p_i = N_i/N_T\). When all species have identical abundances and
\(p_i = 1/S\), where \emph{S} is species richness, the both synchrony
values equal 1/S (Loreau and {{de Mazancourt}} 2008). The prediction
represented in Equation S19 is Equation 3 in the main text, which we
refer to as \(\phi_{R,\mathcal{M}_D}\).

@@

\begin{equation}
\phi_R = \frac{\sum_{i,j} \text{cov}(u_{ei}, u_{ej})}{S^2}
\end{equation}

\noindent The prediction represented in Equation S21 is Equation 4 in
the main text, which we refer to as \(\phi_{R,\mathcal{M}_E}\). If we
know the covariance matrix of the species environmental responses, we
can calculate the above expectations directly. Note that the
environmental responses are normalized in the above equations, therefore
the covariances are correlations in the above equations.
